---
title: "DTIs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DTIs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The **uniprot_drug_data** function retrieves gene names and organism information of drugs from UniProt and returns the result as a data frame. The function takes a character vector of drug names as an input and returns a data frame containing the accession number, gene names, organism name, review status and the drug name.

# Usage

```{r usage}
library(DTIs)
uniprot_drug_data(drug = c("Aceclofenac", "Alverine"))
```

The above code will return a data frame containing the accession number, gene names, organism name, review status and the drug name for the drugs in the character vector passed to the function.

## Example

Retrieve data for Aceclofenac and Benzthiazide:

```{r Example, warning=FALSE}
# Retrieve data for Aceclofenac and Benzthiazide
drug <- c("Aceclofenac", "Alverine")
result <- uniprot_drug_data(drug)

# Save the result to a CSV file
write.csv(x = result, file = "./targets.csv", sep = ",", row.names = FALSE, col.names = TRUE)
```

This will return the gene names and organism information for the drugs **Aceclofenac** and **Alverine**, then save the result to a CSV file named *targets.csv*.
